### 2017-04-21 paper/jfp-submission/interactive-short.tex
let's see what the JFP format looks like..
fiddling with figures..

\begin{figure}[t]
\centering
\includegraphics[width=\linewidth]{fac-steps-new.png}
\caption{A sequence of interactions with the trace of
  \texttt{fac 1}. The stuck term is red, in each node the redex is
  highlighted. Thick arrows denote a multi-step transition, thin arrows
  denote a single-step transition. We start in step 1. In step 2 we jump
  forward from the witness to the next function call. In step 3 we step
  into the recursive \texttt{fac 0} call, which spawns a new ``thread''
  of execution. In step 4 we take a single step forward from
  \texttt{fac 0}.}
\label{fig:nanomaly-factorial}
\end{figure}

@@

\paragraph{Jump Compression}
%
A \emph{jump compressed} trace is one whose edges are limited to forward
or backward jumps.
% (The sizes of these traces is equal to the jump
% metric below.)
%
In our experience, jump compression abstracts many details of the
computation that are often uninteresting or irrelevant to the
explanation.
%
In particular, jump compressed traces hide low-level operations and
summarize function calls as call-return pairs, see
Figure~\ref{fig:fac-jump} for a variant of @fac@ that implements the
subtraction as a function call instead of a primitive.
%
\begin{figure}[t]
\centering
\includegraphics[height=2in]{fac-minus.png}
\caption{Jump-compressed trace of \texttt{fac 1} with subtraction
  implemented as a function call.}
\label{fig:fac-jump}
\end{figure}
%
Once the user has identified an interesting call-return pair, they can
step into the call and proceed with more fine-grained steps.
%
% Expanding the initial visualization to a jump-compressed trace is often
% an ideal first step;
% % expanding a jump-compressed traces ideal for the initial state of the
% they provide a concise overview of the execution and allow the user to
% step directly into an interesting function call, at which point the can
% proceed with more fine-grained steps.
%
Note that jump compressed traces are not quite the same as
stack-traces as they show \emph{all} function calls, including
those that returned successfully.
%
% For example, the display on the bottom-left in Figure~\ref{fig:factorial} shows
% a jump-compressed trace, of size 4. The full trace for
% the same example (on the right of the Figure~\ref{fig:factorial}) has size 19.

>>>>

\begin{figure}[t]
\centering
\includegraphics[height=4in]{fac-steps-new.png}
\caption{A sequence of interactions with the trace of
  \texttt{fac 1}. The stuck term is red, in each node the redex is
  highlighted. Thick arrows denote a multi-step transition, thin arrows
  denote a single-step transition. We start in step 1. In step 2 we jump
  forward from the witness to the next function call. In step 3 we step
  into the recursive \texttt{fac 0} call, which spawns a new ``thread''
  of execution. In step 4 we take a single step forward from
  \texttt{fac 0}.}
\label{fig:nanomaly-factorial}
\end{figure}

@@

\paragraph{Jump Compression}
%
A \emph{jump compressed} trace is one whose edges are limited to forward
or backward jumps.
% (The sizes of these traces is equal to the jump
% metric below.)
%
In our experience, jump compression abstracts many details of the
computation that are often uninteresting or irrelevant to the
explanation.
%
In particular, jump compressed traces hide low-level operations and
summarize function calls as call-return pairs, see
Figure~\ref{fig:fac-jump} for a variant of @fac@ that implements the
subtraction as a function call instead of a primitive.
%
\begin{figure}[t]
\centering
\includegraphics[height=2in]{fac-minus.png}
\caption{Jump-compressed trace of \texttt{fac 1} with subtraction
  implemented as a function call.}
\label{fig:fac-jump}
\end{figure}
%
Once users have identified interesting call-return pairs, they can
step into those calls and proceed with more fine-grained steps.
%
% Expanding the initial visualization to a jump-compressed trace is often
% an ideal first step;
% % expanding a jump-compressed traces ideal for the initial state of the
% they provide a concise overview of the execution and allow the user to
% step directly into an interesting function call, at which point the can
% proceed with more fine-grained steps.
%
Note that jump compressed traces are not quite the same as
stack-traces as they show \emph{all} function calls, including
those that returned successfully.
%
% For example, the display on the bottom-left in Figure~\ref{fig:factorial} shows
% a jump-compressed trace, of size 4. The full trace for
% the same example (on the right of the Figure~\ref{fig:factorial}) has size 19.

### 2017-04-21 paper/jfp-submission/semantics.tex
fiddling with figures..

%   % \force{v}{\subst{\tsu}{\thole}}{\vsu}{\tsu} & \mbox{if}\ \thole \in dom(\tsu) \\
%   % \triple{v}{\vsu}{\extendsu{\tsu}{\thole}{\typeof{v}}} & \mbox{otherwise} \\
% \end{cases} \\
\force{\vhole{\thole}}{t}{\vsu}{\tsu} & \defeq % \hspace{-1ex}
\begin{cases}
  \triple{v}{\vsu}{\tsu'}    & \textbf{if} \begin{array}{l} v = \lookupsu{\vsu}{\vhole{\thole}}, \\
                                         \tsu' = \unify{\{\thole, t, \typeof{v}\}}{\tsu}\end{array} \\
  \triple{\stuck}{\vsu}{\tsu} & \textbf{if} \begin{array}{l} v = \lookupsu{\vsu}{\vhole{\thole}}\end{array} \\
  \triple{v}{\extendsu{\vsu}{\vhole{\thole}}{v}}{\tsu'} & \textbf{if} \begin{array}{l} \tsu' = \unify{\{\thole, t\}}{\tsu}, \\ v = \gen{t}{\tsu'} \end{array}\\
\end{cases}  \\
% \begin{cases}
%   \triple{\lookupsu{\vsu}{\ehole}}{\vsu}{\tsu} & \mbox{if}\ \ehole \in dom(\vsu), \hastype{\lookupsu{\vsu}{\ehole}}{t} \\
%   \triple{\stuck}{\vsu}{\tsu}                  & \mbox{if}\ \ehole \in dom(\vsu) \\
%   \triple{v}{\extendsu{\vsu}{\ehole}{v}}{\tsu}   & v = \gen{t}\\
% \end{cases} \\
 % \begin{array}{l}
    % \mathtt{if}\ i \in \vsu\ \mathtt{then}\ \triple{\vsu(i)}{\vsu}\ \mathtt{else} \\
         % \elet{v}{\gen{t}}{\triple{v}{\ehole{i} \mapsto v}}
  % \end{array} \\
\force{n}{\tint}{\vsu}{\tsu}     & \defeq \triple{n}{\vsu}{\tsu} \\
\force{b}{\tbool}{\vsu}{\tsu}    & \defeq \triple{b}{\vsu}{\tsu} \\
\force{\efun{x}{e}}{\tfun}{\vsu}{\tsu} & \defeq \triple{\efun{x}{e}}{\vsu}{\tsu} \\
\force{\epair{v_1}{v_2}}{\tprod{t_1}{t_2}}{\vsu}{\tsu} & \defeq \triple{\epair{v_1}{v_2}}{\vsu}{\tsu''} & \hspace{-42mm} \textbf{if} \begin{array}{l} \tsu' = \unify{\{\typeof{v_1}, t_1\}}{\tsu},\\ \tsu'' = \unify{\{\typeof{v_2}, t_2\}}{\tsu'} \end{array} \\
\force{\vleaf{t_1}}{\ttree{t_2}}{\vsu}{\tsu} & \defeq \triple{\vleaf{t_1}}{\vsu}{\tsu'} & \hspace{-42mm} \textbf{if} \begin{array}{l} \tsu' = \unify{\{t_1, t_2\}}{\tsu} \end{array}\\
\force{\vnode{t_1}{v_1}{v_2}{v_3}}{\ttree{t_2}}{\vsu}{\tsu} \hspace{-3mm} & \defeq \triple{\vnode{t_1}{v_1}{v_2}{v_3}}{\vsu}{\tsu'} & \hspace{-42mm} \textbf{if} \begin{array}{l} \tsu' = \unify{\{t_1, t_2\}}{\tsu} \end{array} \\
\force{v}{t}{\vsu}{\tsu} & \defeq \triple{\stuck}{\vsu}{\tsu}
\end{array}
\]
\caption{Narrowing values}
\label{fig:narrow}
\end{figure}
%
%While a hole may map to a value that \emph{contains} another hole, \eg a
%lambda or a tree, it may not map \emph{directly} to another hole,
As the value substitution is normalized, in the first case of \forcesym\ we
do not need to \forcesym\ the result of the substitution, the sub-hole
will be narrowed when the context demands it.

@@

\begin{cor}{\textbf{[Witness Generation]}}
\label{thm:generation}
  If $$\genWitness{k}{e} = \triple{\eapp{e}{v_1 \ldots v_n}}{\vsu}{\tsu},\ldots$$
  then for all types $t_1 \ldots t_n$ there exist values $w_1 \ldots w_n$ such that
  $\steps{\eapp{e}{w_1 \ldots w_n}}{\emptysu}{\emptysu}{\stuck}{\vsu'}{\tsu'}$.
\end{cor}
\begin{proof}
  For any function $f$ of multiple arguments, we can define $f'$ to be
  the uncurried version of $f$ that takes all of its arguments as a single
  nested pair, and then apply Theorem~\ref{thm:soundness} to $f'$.
\end{proof}

>>>>

%   % \force{v}{\subst{\tsu}{\thole}}{\vsu}{\tsu} & \mbox{if}\ \thole \in dom(\tsu) \\
%   % \triple{v}{\vsu}{\extendsu{\tsu}{\thole}{\typeof{v}}} & \mbox{otherwise} \\
% \end{cases} \\
\force{\vhole{\thole}}{t}{\vsu}{\tsu} & \defeq % \hspace{-1ex}
\begin{cases}
  \triple{v}{\vsu}{\tsu'}    &\ \textbf{if} \begin{array}{l} v = \lookupsu{\vsu}{\vhole{\thole}}, \\
                                         \tsu' = \unify{\{\thole, t, \typeof{v}\}}{\tsu}\end{array} \\
  \triple{\stuck}{\vsu}{\tsu} &\ \textbf{if} \begin{array}{l} v = \lookupsu{\vsu}{\vhole{\thole}}\end{array} \\
  \triple{v}{\extendsu{\vsu}{\vhole{\thole}}{v}}{\tsu'} &\ \textbf{if} \begin{array}{l} \tsu' = \unify{\{\thole, t\}}{\tsu}, \\ v = \gen{t}{\tsu'} \end{array}\\
\end{cases}  \\
% \begin{cases}
%   \triple{\lookupsu{\vsu}{\ehole}}{\vsu}{\tsu} & \mbox{if}\ \ehole \in dom(\vsu), \hastype{\lookupsu{\vsu}{\ehole}}{t} \\
%   \triple{\stuck}{\vsu}{\tsu}                  & \mbox{if}\ \ehole \in dom(\vsu) \\
%   \triple{v}{\extendsu{\vsu}{\ehole}{v}}{\tsu}   & v = \gen{t}\\
% \end{cases} \\
 % \begin{array}{l}
    % \mathtt{if}\ i \in \vsu\ \mathtt{then}\ \triple{\vsu(i)}{\vsu}\ \mathtt{else} \\
         % \elet{v}{\gen{t}}{\triple{v}{\ehole{i} \mapsto v}}
  % \end{array} \\
\force{n}{\tint}{\vsu}{\tsu}     & \defeq \triple{n}{\vsu}{\tsu} \\
\force{b}{\tbool}{\vsu}{\tsu}    & \defeq \triple{b}{\vsu}{\tsu} \\
\force{\efun{x}{e}}{\tfun}{\vsu}{\tsu} & \defeq \triple{\efun{x}{e}}{\vsu}{\tsu} \\
\force{\epair{v_1}{v_2}}{\tprod{t_1}{t_2}}{\vsu}{\tsu} & \defeq \triple{\epair{v_1}{v_2}}{\vsu}{\tsu''} & \hspace{-43.5mm} \textbf{if} \begin{array}{l} \tsu' = \unify{\{\typeof{v_1}, t_1\}}{\tsu},\\ \tsu'' = \unify{\{\typeof{v_2}, t_2\}}{\tsu'} \end{array} \\
\force{\vleaf{t_1}}{\ttree{t_2}}{\vsu}{\tsu} & \defeq \triple{\vleaf{t_1}}{\vsu}{\tsu'} & \hspace{-43.5mm} \textbf{if} \begin{array}{l} \tsu' = \unify{\{t_1, t_2\}}{\tsu} \end{array}\\
\force{\vnode{t_1}{v_1}{v_2}{v_3}}{\ttree{t_2}}{\vsu}{\tsu} \hspace{-3mm} & \defeq \triple{\vnode{t_1}{v_1}{v_2}{v_3}}{\vsu}{\tsu'} & \hspace{-43.5mm} \textbf{if} \begin{array}{l} \tsu' = \unify{\{t_1, t_2\}}{\tsu} \end{array} \\
\force{v}{t}{\vsu}{\tsu} & \defeq \triple{\stuck}{\vsu}{\tsu}
\end{array}
\]
\caption{Narrowing values}
\label{fig:narrow}
\end{figure}
%
%While a hole may map to a value that \emph{contains} another hole, \eg a
%lambda or a tree, it may not map \emph{directly} to another hole,
As the value substitution is normalized, in the first case of \forcesym\ we
do not need to \forcesym\ the result of the substitution, the sub-hole
will be narrowed when the context demands it.

@@

\begin{cor}{\textbf{[Witness Generation]}}
\label{thm:generation}
  If $\genWitness{k}{e} = \triple{\eapp{e}{v_1 \ldots v_n}}{\vsu}{\tsu},\ldots$
  then for all types $t_1 \ldots t_n$ there exist values $w_1 \ldots w_n$ such that
  $\steps{\eapp{e}{w_1 \ldots w_n}}{\emptysu}{\emptysu}{\stuck}{\vsu'}{\tsu'}$.
\end{cor}
\begin{proof}
  For any function $f$ of multiple arguments, we can define $f'$ to be
  the uncurried version of $f$ that takes all of its arguments as a single
  nested pair, and then apply Theorem~\ref{thm:soundness} to $f'$.
\end{proof}
